Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2021-12-05 energy-planning.tex
fixes and polishing (2)

\begin{abstract}
  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots, which plans in-flight a coverage path and simultaneously schedules onboard computational tasks. It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model. The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool. Accounting for uncertainty, an initial ``plan-schedule'' is replanned and rescheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Defs.~\ref{def:plan}--\ref{def:trigs} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$. Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in the agricultural use case, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.

@@

Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ indicates the set of integers. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}. $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and 
after Definition~\ref{def:trigs}.

@@

The notation $[\,\cdot\,]$ indicates positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.

The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ indicates the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

@@

Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\ref{def:trigs}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\Gamma_2,\dots$ but $\Gamma_0$, the stating stage. The constraint sets $\mathcal{C}_{1,1},\mathcal{C}_{2,1},\dots$ forms the area where it is possible to alter the paths $\varphi_1,\varphi_2,\dots$ with the parameters $c_{1,1},c_{2,1},\dots$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

Here, $c_i$ indicates a row vector that contains both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$, where $\,\cdot\,'$ is the transpose of $\cdot\,$. The path parameters in the definition have a constant distance per each value in $[n]_{>0}$, i.e., 
\begin{equation}\label{eq:primitive}\begin{split}
  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
\end{split}\end{equation}
holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$. $e_j\in\mathbb{R}$ given a shift $\mathbf{d}$, initial point $\mathbf{p}$, and initial value of path parameters $c_1^\rho$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\varphi_2,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{\geq 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\vspace*{-2ex}
\subsection{Problem formulation}
\label{sec:pbfor}

@@

For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ indicates the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
.

\begin{pb}[Planning problem]
  \label{pb}
  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}. The \emph{planning problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
\end{pb}

@@

\vspace*{-1ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of given path and computations parameters on the battery at future time instants. To this end, Secs.~\ref{sec:mod-mot}--\ref{sec:mod-bat} provide models for the motion and computations energies and battery.

@@

Let us return to the collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift. Energy data exhibit periodic behavior, an observation further backed by the power spectrum analysis. It indicates that to model the energy, three frequencies are adequate.

@@

The model in Equation~(\ref{eq:fourier}) does not the quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules results in different instantaneous energy. For this latter purpose, we use another model
\begin{subequations}\label{eq:state-perf}\begin{align}
  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t),\label{eq:state-perf-q}\\
  y(t)&=C\mathbf{q}(t),\label{eq:state-perf-y}
\end{align}\end{subequations}
where $y(t)\in\mathbb{R}$ is the instantaneous energy consumption. The state $\mathbf{q}\in\mathbb{R}^m$ with $m:=2r+1$ contains energy coefficients
\begin{equation}
  \mathbf{q}(t)=\begin{bmatrix}
    \alpha_0(t) & \alpha_1(t) & \beta_1(t) & \cdots & \alpha_r(t) & \beta_r(t)
  \end{bmatrix}'.
\end{equation}

@@

Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains proofs of Lems.~\ref{lem:eqv}--\ref{lem:new}.

Using the same notation from Lemma~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
\begin{equation}
  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
\end{equation}
for all time instants. $\hat{\mathbf{u}}$ is then a scale transformation
\begin{equation}
  \hat{\mathbf{u}}(t):=\mathrm{diag}(\nu_i)c_i(t)+\tau_i
\end{equation}
where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere. $\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Def.~\ref{def:stage}) to time and power domains.

Let us assume that the time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$.

Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with scaling factors
\begin{subequations}\label{eq:scale-comp}\begin{align}
  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
\end{align}\end{subequations}
$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Sec.~\ref{sec:mod-com} and quantifies the power of the computing hardware.

The input matrix then includes the change in energy, i.e.,
\begin{equation}\label{eq:mat_B}
  B=\begin{bmatrix}
      0^{1\times\rho} & 1      & \cdots & 1      \\
      0^{1\times\rho} & 0      & \cdots & 0      \\ 
      \vdots          & \vdots & \ddots & \vdots \\
      0^{1\times\rho} & 0      & \cdots & 0   
  \end{bmatrix},
\end{equation}
where $B\in\mathbb{R}^{m\times n}$ contains zeros except the first row where the first $\rho$ columns are still zeros and the remaining $\sigma$ are ones.

\subsection{Energy model for the computations}
\label{sec:mod-com}

Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware or software specific parameters. This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis aiding to quantify the computations energy of any combination of computations $c_i^\sigma$ withing the bounds (see Def.~\ref{def:stage}).

The model relies on an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source M.I.T. license. It is segmented into two layers. In the \emph{measurement layer} the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piece-wise linear regression.

Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperometer, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.

@@

\begin{defn}[Predictive layer]\label{def:pred}
  Given a measuring device and computations parameters the \emph{predictive layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns and energy measure.
\end{defn}

The energy measures in Defs.~\ref{def:meas}--\ref{def:pred} can be either average or overall energy. Additionally, the tool supports the measures of battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}. The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}) assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where the notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. The measuring device in both $\mathbf{g}$ and $g$ is implicit.

@@

The battery model predicts the battery SoC in function of a given load for future time instants. There are multiple possible models in the literature~\cite{rao2003battery}, with varying accuracy, complexity, and easy of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of ease of implementation and accuracy.

We model a Li-ion battery of an aerial robot flying with an abstract model referred to as ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.

@@

Appendix~\ref{app:proof-bat} contains a proof of Lem.~\ref{lem:bat}.

Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$. Let us re-evaluate the output constraint with Lem.~\ref{lem:bat}.

\begin{defn}[Output constraint]
  \label{def:const}
  \begin{equation*}
    \mathcal{Y}(t):=\{y\mid y\in[0,b(y(t))Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
  \end{equation*}
  is the \emph{output constraint}, where $b(y(t))Q_cV$ is the maximum instantaneous energy consumption.
\end{defn}

@@

\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.25\columnwidth}
    \caption{The alteration of the path parameter $c_{1,1}$, the radius of the circle (it corresponds to the alteration of the plan in Fig.~\ref{fig:il-abs}).}
    \label{fig:tee1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.7\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj2.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Planning-Scheduling}  %
\label{sec:algo}               %
                               %
This section solves Problems~\ref{pb:cov-pb}--\ref{pb}, i.e., derives a plan in Sec.~\ref{sec:cov-algo}, and re-plans the plan energy-wise in Sec.~\ref{sec:repla-algo}.

\subsection{Coverage path planning}
\label{sec:cov-algo}

@@

To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius. It is similar to another motion in the literature termed \emph{Zamboni motion}~\cite{araujo2013multiple},
but additionally allows variable CPP at the very core of this work. The motion, termed \emph{Zamboni-like motion}, is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}). Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates an edge formed by vertices $v_x,v_y$.

Algorithm~\ref{alg2} illustrates the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$.

@@

          \vspace*{.8ex}
          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\ref{def:stage}}\label{alg2:last}

@@

\subsection{Coverage re-planning-scheduling}
\label{sec:repla-algo}

>>>>

\begin{abstract}
  The letter presents a planning-scheduling approach for battery-powered autonomous aerial robots, which plans in-flight a coverage path and simultaneously schedules onboard computational tasks. It derives a novel variable coverage motion robust to airborne constraints and an empirically motivated differential periodic energy model. The model is enhanced with the time and energy contribution of the path and tasks, utilizing a previously proposed automatic modeling tool. Accounting for uncertainty, an initial ``plan-schedule'' is re-planned and re-scheduled in the function of the battery, exploiting all the available resources yet avoiding possible in-flight failure in case of unexpected battery drops, e.g., due to adverse atmospheric conditions.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Formulation}  %
\label{sec:prob}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.35\columnwidth}
    \caption{Defs.~\ref{def:plan}--\hyperref[def:trigs]{4} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_1},\dots$ are triggering points in which proximity happens change of stages $\Gamma_1,\dots$. Each contains a path function $\varphi_1,\dots$ and parameters to alter the path and schedule $c_{1,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

Before defining the problem of energy-aware planning-scheduling in Sec.~\ref{sec:pbfor}, Sec.~\ref{sec:prelim} provides necessary preliminaries. For CPP and, e.g., pattern detections in precision agriculture, we assume that aerial robot travels a \emph{plan} with information about the path and the schedule.

@@

Here, $\Gamma_i$ is a \emph{stage}, and $\mathbb{Z}$ denotes the set of integers. At each stage, the aerial robot travels a path and runs a schedule on the computing hardware. Both are to be altered in Sec.~\ref{sec:algo} within given boundaries with \emph{path}- and \emph{computations}-specific \emph{parameters}. $\varepsilon_i$ is a stage-dependent value detailed %along with $\mathbf{p}_{\Gamma_i}$ in and 
after Definition~\ref{def:trigs}.

@@

The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$.
For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive.

The function $\varphi_i$ is a \emph{path function} specifying the path. These are stage-dependent mathematical functions the aerial robot tracks as it travels %the motion for 
the coverage. The notation $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ denotes the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

@@

Fig.~\ref{fig:traj1} illustrates the concepts in Defs.~\ref{def:plan}--\hyperref[def:trigs]{4}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$. %The constraint set $\mathcal{C}_{4,1}$ forms the area where 
It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
\begin{equation}\label{eq:primitive}\begin{split}
  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
\end{split}\end{equation}
holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$. $e_j\in\mathbb{R}$ given a shift $\mathbf{d}$, initial point $\mathbf{p}$, and initial value of path parameters $c_1^\rho$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Def.~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instant $\in\mathbb{R}_{> 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is completed, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

\vspace*{-2ex}
\subsection{Energy-aware planning-scheduling problem}
\label{sec:pbfor}

@@

For a set $\mathbb{X}$, the notation $|\mathbb{X}|$ denotes the cardinality of $\mathbb{X}$%, i.e, $|\mathbb{X}|:=\sum_{x\in\mathbb{X}}1$
.

\begin{pb}[Re-planning-scheduling problem]
  \label{pb}
  Consider an initial plan $\Gamma$ in Def.~\ref{def:plan}. The \emph{re-planning-scheduling problem} is the problem of finding the optimal configuration of path and computations parameters $c_i(t),\,\forall i\in\{1,2,\dots\}$ under energy constraints and uncertainty at each time step $t$.
\end{pb}

Here, $c_i$ denotes a row vector with both the path and computations parameters in sequence, i.e., $c_i:=[\begin{matrix}\,c_i^\rho & c_i^\sigma\,\end{matrix}]'$. The notation $\,\cdot\,'$ denotes the transpose of $\cdot\,$.

@@

\vspace*{-1ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to Pb.~\ref{pb} requires accurate energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants. To this end, Secs.~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the motion and computations energies and battery.

@@

Let us return to the collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs}, illustrating the energy of a coverage plan $\Gamma$ with four primitive path functions iterated with a shift. The data exhibit periodic behavior, an observation further backed by the power spectrum analysis. It indicates that to model the energy, three frequencies are adequate.

@@

The model in Equation~(\ref{eq:fourier}) does not quantify the contribution of path and computations parameters $c_i$, where, e.g., different schedules result in different instantaneous energy. For this latter purpose, we use another model
\begin{subequations}\label{eq:state-perf}\begin{align}
  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t),\label{eq:state-perf-q}\\
  y(t)&=C\mathbf{q}(t),\label{eq:state-perf-y}
\end{align}\end{subequations}
where $y(t)\in\mathbb{R}$ is the instantaneous energy consumption. The state $\mathbf{q}\in\mathbb{R}^m$ with $m:=2r+1$ contains energy coefficients
\begin{equation}
  \mathbf{q}(t)=\begin{bmatrix}
    \alpha_0(t) & \alpha_1(t) & \beta_1(t) & \cdots & \alpha_r(t) & \beta_r(t)
  \end{bmatrix}'.
\end{equation}

@@

Appendices~\ref{app:proof-eqv}--\ref{app:proof-new} contains the proofs of Lemmas.~\ref{lem:eqv}--\hyperref[lem:new]{2}.

Using the same notation from Lem.~\ref{lem:new}, the nominal control in Eq.~(\ref{eq:state-perf})
\begin{equation}
  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
\end{equation}
for all time instants. $\hat{\mathbf{u}}$ is then a scale transformation
\begin{equation}
  \hat{\mathbf{u}}(t):=\mathrm{diag}(\nu_i)c_i(t)+\tau_i
\end{equation}
where $\mathrm{diag}(\,\cdot\,)$ is a diagonal matrix with items of a set $\cdot$ on the diagonal and zeros elsewhere. $\nu_i:=\begin{bmatrix}\nu_{i,1}&\cdots&\nu_{i,n}\end{bmatrix}'$ and $\tau_i:=\begin{bmatrix}\tau_{i,1}&\cdots&\tau_{i,n}\end{bmatrix}'$ are scaling factors with $n:=\rho+\sigma$ that transform parameters domain (see Def.~\ref{def:stage}) to time and power domains.

Let us assume for ease of notation that the coverage time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$.

Similarly to Eq.~(\ref{eq:scale-traj}), computations parameters $c_i^\sigma$ can be transformed into an instantaneous energy measure with %scaling factors
\begin{subequations}\label{eq:scale-comp}\begin{align}
  \nu_{i,j}&=(g(\overline{c}_{i,j})-g(\underline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j}),\\
  \tau_{i,j}&=\underline{c}_{i,j}(g(\underline{c}_{i,j})-g(\overline{c}_{i,j}))/(\overline{c}_{i,j}-\underline{c}_{i,j})+g(\underline{c}_{i,j}),
\end{align}\end{subequations}
$\forall j\in[\rho+1,n]$. The function $g$ is detailed in Sec.~\ref{sec:mod-com} and quantifies the power of the computing hardware.

The input matrix then includes the change in energy, i.e.,
\begin{equation}\label{eq:mat_B}
  B=\begin{bmatrix}
      0^{1\times\rho} & 1      & \cdots & 1      \\
      0^{1\times\rho} & 0      & \cdots & 0      \\ 
      \vdots          & \vdots & \ddots & \vdots \\
      0^{1\times\rho} & 0      & \cdots & 0   
  \end{bmatrix},
\end{equation}
where $B\in\mathbb{R}^{m\times n}$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones.

\vspace*{-1.5ex}
\subsection{Energy model for the computations}
\label{sec:mod-com}

Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters. This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Def.~\ref{def:stage}).

The model compromises an automatic modeling and profiling tool~\cite{seewald2019coarse} named \powprof{} distributed~\cite{powprofiler} under the open-source MIT license. It is segmented into two layers. In the \emph{measurement layer}, the tool measures a discrete set of computations parameters and infers the energy of the remaining in the \emph{predictive layer} via a piecewise linear regression.

Let us assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.

@@

\begin{defn}[Predictive layer]\label{def:pred}
  Given a measuring device and computations parameters, the \emph{predictive layer} is the function $g:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\rightarrow\mathbb{R}$ that returns an energy measure.
\end{defn}

The energy measures in Defs.~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall. Additionally, the tool supports the battery state of charge (SoC) detailed in Sec.~\ref{sec:mod-bat}. The function $g$ in Def.~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. The measuring device in both $\mathbf{g}$ and $g$ is implicit.

@@

The battery model predicts the battery SoC in the function of a given load at future time instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity, accuracy, and ease of implementation ranging from accurate but costly physical models~\cite{moura2017battery,marcicki2013design}, to abstract models~\cite{xing2014state,he2011evaluation,hinz2019comparison,mousavi2014various} that have compelling trade-offs in terms of the latter two.

We model a Li-ion battery of an aerial robot in-flight with an abstract ``Rint'' equivalent circuit model (ECM) in the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}.

@@

App.~\ref{app:proof-bat} contains the proof of Lem.~\ref{lem:bat}.

Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, conflicting with the findings in Lem.~\ref{lem:bat}.

\begin{defn}[Output constraint]\label{def:const}
  \begin{equation*}
    \mathcal{Y}(t):=\{y\mid y\in[0,b(y(t))Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
  \end{equation*}
  is the \emph{output constraint}, where $b(y(t))Q_cV$, the maximum instantaneous energy consumption measured in watts, is derived from Lem.~\ref{lem:bat}.
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Planning-Scheduling}  %
\label{sec:algo}               %
                               %
\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.25\columnwidth}
    \caption{Alteration of the path parameter $c_{i,1}$, the radius of the circle (i.e., the alteration of the plan in Fig.~\ref{fig:il-abs}).
    }
    \label{fig:tee1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.7\columnwidth}
    \centering
    \vspace*{-4.5ex}
    \input{\figpath/new/traj2.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

The section solves Problems~\ref{pb:cov-pb}--\hyperref[pb]{2}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise %respectively
in Secs.~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.

\vspace*{-1.4ex}
\subsection{Coverage}
\label{sec:cov-algo}

@@

To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius. It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work. The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Def.~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$ (see Fig.~\ref{fig:zambo}).

Let us assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$. 
Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$. The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$. Nonetheless, complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.

@@

          \vspace*{.8ex}
          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Defs.~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}

@@

\vspace*{-1.4ex}
\subsection{Re-planning-scheduling}
\label{sec:repla-algo}
